% Group: 	2
% Name: 	Coding Pharaohs
% Document: 	Minutes of the seventh client meeting
% Author:	Abdulaziz Alhulayfi
% Date: Tuesday 8 October 2013

\documentclass[12pt, a4paper]{article}
\topmargin -1cm
\title{Minutes of the Seventh Client Meeting}
\author{\textsc{Coding Pharaohs} (Group 2)}
\date{October 9, 2013}

\begin{document}
\maketitle

\begin{tabbing}
\textbf{Chair}~~~~~~~~\=Yu Hong           \\
\textbf{Secretary}    \>Abdulaziz Alhulayfi     \\
\textbf{Members}      \>Yifei Pei  \\
                      \>Bowen Tao           \\
                      \>Jianqiu Li           \\
                      \>Metthew Nestor            \\
\textbf{Apologies}    \>None                \\
\end{tabbing}

\section{Time and Place}

The seventh client meeting for Software Engineering and Project was held in \textbf{Ingkarni
Wardli, Room 462 \textnormal{at} 2:09pm \textnormal{on} Tuesday 9 October 2013}.

\section{Quorum Announcement}

Having established that all members were present, the meeting was declared open.

\section{Summary of Previous Meeting}

Mr.~Yifei Pei presented the software design document, which contains an overview of the system and its architecture. The architecture style which has been used for this project is Pipe-and-Filter architecture style. Mr.Yifei demonstrated why this particular style was used. Mr.~Yefei Pei went on to talk about the FSM and how the switching between manual and AI modes is controlled. He also demonstrated the new design for the data structure. Mr. Yu Hong presented week 9 milestone. The client was overall happy with the SDD presentation.


\section{Group Milestone: Displaying traveled angle and distance}

\subsection{Overview}

Mr.~Yu Hong showed the client the first part of week 9 milestone and that is to display the traveled angle and distance in real time.

\subsection{Detailed Presentation}

The demonstration showed the client the displaying of traveled distance in cm and the degree of angle rotation. The traveled distance has not been tested in terms of accuracy which will be tested during the following weeks, however the demonstration was initialy good.

\section{Group Milestone: Manual road closure marking}

\subsection{Overview}

Mr.~Yu Hong showed the client the manual road closure marking.

\subsection{Detailed Presentation}

The demonstration showed the client how the robot can manually mark road closures. That is to use the GUI directions buttons and marking button to mark the road closures. The road closures are marked as lines. 

\section{Further features of the robot: Speed bar on the GUI}

\subsection{Overview}

The client asked for more features of the robot, so the group showed some features that should be presented for the milestone of Week 9 to the client. \\

\subsection{Detailed Presentation}

The new feature that was showed to the client is to create a speed bar to control the speed of the robot from the GUI. Mr. Yu showed the client an example of how the speed can be changed from 5 cm/s to 10cm/s.

\section{Group Milestone: A1 size map with basic features prepared}

\subsection{Overview}

Mr.~Yifei Pei presented a sample of A1 size map with basic features.

\subsection{Detailed Presentation}

Mr.~Yifei Pei showed the client an A1 size map with edges, roads and dangerous zone. He also informed the client of upcoming updates to the map such as undiscovered areas and intersections.

\section{Meeting Feedback}
\begin{itemize}
 
 \item For the SDD presentation, the client had a few questions to ask for clarification regarding the software architecture design which had been answered by Mr. Yifei Pei.
 \item For the display of the traveled distance, the client emphasized on the accuracy of the distance as this is critical in terms of the robot safety and the location of the closures to be marked.
 \item For the representation of the robot on GUI map, the client suggested a clear representation of which direction the robot is traveling. This is an important part of the design as the operator might quickly need to know where the robot is heading.
\item Finally, the client was overall pleased with what the group presented for week 9 milestone.
\end{itemize}

\section{SDD Feedback}

The group got an overall mark of 57.5 in the first version of the software design document. The client handed in to the group the marking sheet which shows that some major improvements are needed specially on the host side design.

\section{Adjournment}
The next meeting is a group meeting to be held in Ingkarni Wardli, Room 462 at 2pm on Thursday 10 October 2013, and the next client meeting will be held at the same place at 2.30pm Monday 14 September 2013.\\
\\
The meeting closed at 2:37pm.
\end{document}
