%%%%%%Agenda for client meeting Monday 14 October 2013. Prepared by Abdulaziz Alhulayfi 12/10/13.
\documentclass[11pt, a4paper]{article}
\usepackage{times}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

%%% page parameters
\oddsidemargin 0 cm
\evensidemargin 0 cm
\textwidth 16 cm
\topmargin -2.5 cm
\textheight 25.5 cm

\renewcommand{\baselinestretch}{1.4}\normalsize
\setlength{\parskip}{0pt}


\begin{document}

%%%mention the number, time, and venue of the meeting
\noindent The {\em 9th} client meeting for Software Engineering Group 2. {\em Weekly} project meeting will be held in {\bf BCS Software Lab, Room 462, Ingkarni Wardli} \textnormal{at} 2:30pm  \textnormal{on} Monday 21 October 2013.


\vspace*{15pt}

\begin{center}
\huge \bf Agenda
\end{center}



\section*{Chair: Bowen Tao \large (a1642362)}

\vspace*{15pt}


\section{Presentation}

\begin {item}

\item  For Mystery Presentation, each member in group 2 will act a role based on the case of Killer Robot. The detail is following:\\
\\
\textbf{Abdulaziz Alhulayfi} will present Jan Anderson, who is the former programmer and analyst at Silicon Techtronics and she opposed the use of the waterfall model on the robot project and was fired for her honesty.\\
\\
\textbf{Bowen Tao} will present Randy Samuels, who is the programmer and he wrote the program code that caused the Robbie CX30 robot to oscillate wildly, killing the robot operator, Bart Matthews.\\
\\
\textbf{Hong Yu} will present Michael Waterson, who is the president and CEO of Silicon Techtronics. He placed Sam Reynolds in charge of the Robbie CX30 project as a cost-saving measure. He contributed generously to Jane McMurdock's re-election campaign, and hired Dr. Wesley Silber to conduct an investigation into software quality assurance at Silicon Techtronics.\\
\\
\textbf{Jianqiu Li} will present Cindy Yardley, who is the Silicon Techtronics employee and software tester and she admitted to faking software tests in order to save the jobs of her co-workers.\\
\\
\textbf{Matthew Nestor} will present Sam Reynolds, who is the CX30 Project Manager. Although background was in data processing, he was put in charge of the Robbie CX30 project, much to Ray Johnson's chagrin. He was committed to the waterfall model of software development.\\
\\
\textbf{Yifei Pei} will present Max Worthington, who is the Chief security officer for Silicon Techtronics and he monitored electronic mail communications among the employees and thus exposed Cindy Yardley.\\
\end {itemize}




%%%any schedules for this meeting should go next, each with a separate section.
%%%for example, the first meeting is about requirement elicitation, like the following.

%%%if there are more subissues, make them as subsections.


%%%finally, specifies time of next meeting
\section{Date of Next Meeting}
\noindent Next meeting to be held on Monday 28 October 2013 at 2:30pm.


\end{document}